---
title: "Homework 2 - Sept 21"
author: "Your name here"
date: "DATA 2401"
output: html_document
---

Due Sept 28th at 1pm (class time). Turn in your zipped html (or pdf) of this file. Make sure to put the author name as your own, and change the file name to HW2_yourlastname.html

For all questions below, you should not "hard code" whenever possible. For example, if I have the following vector, and ask for a new vector of just the "a"s: 

```{r}
vec <- c("a", "b", "a", "c")

# wrong (technically correct, but hard coded)
new_vec <- vec[c(1,3)]
new_vec

# right (finds the correct indexes using a logical check)
new_vec <- vec[vec == "a"]
new_vec
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the code chunk below: 


1. Create a vector `even` that holds the even numbers from 1 to 100
2.  Using the `all()` function and `%%` (modulo) operator, confirm that all of the numbers in your `even` vector are even

```{r}

```

In the code chunk below: 

3. Create a vector `phone_numbers` that contains the numbers 2, 8, 1, 3, 3, 0, 8, 0, 0, 4
4.  Using indexing, create a vector `prefix` that has the first three elements of `phone_numbers`
5. Using logical indexing, create a vector `small` that has the values of `phone_numbers` that are less than or equal to 5
6. Using logical indexing, create a vector `large` that has the values of `phone_numbers` that are strictly greater than 5
7. Using logical indexing, replace the values in `phone_numbers` that are larger than 5 with the number 5
8. Using logical indexing, Replace every odd-numbered value in `phone_numbers` with the number 0

```{r}

```

In the code chunk below: 

9. Create a vector of 50 simulated dice rolls called `fifty_rolls_1`
10. Create a second vector of 50 simulated dice rolls called `fifty_rolls_2`
11. If you pretend these two die are rolled at the same time, find how many of the 50 rolls are doubles. (doubles are when the two die have the same number)

```{r}
# this function makes it so that your "random" number generator is at the same spot as mine. 
set.seed(1023) ## leave this here to keep the randomness consistent


```


